PineAPPL: EW and mixed QCD--EW corrections for PDF fits

### 2020-07-29 paper/sec-results.tex
Something mor eon Sect.3

\section{Results}
\label{sec:results}

@@

Given one of the measurements discussed in
Sect.~\ref{subsec:processes_and_measurements}, we compute the expectation
value of the corresponding observable in for each bin in two different ways:
directly, by means of {\sc MG5\_aMC}, and a posteriori, by convolving the
fast interpolation grid produced by {\sc PineAPPL} with the PDF set specified
in Sect.~\ref{subsec:computational_settings}. In order to validate the

>>>>

\section{PineAPPL at work: generation and validation of interpolation grids}
\label{sec:results}

@@

For each of the measurements discussed in
Sect.~\ref{subsec:processes_and_measurements}, we compute the expectation
value of the corresponding observable for each kinematic bin in two different
ways: directly, by means of {\sc MG5\_aMC}, and a posteriori, by convolving the
fast interpolation grid produced by {\sc PineAPPL} with the PDF set specified
in Sect.~\ref{subsec:computational_settings}. In the following, we will refer
to the the first result as the {\sc MC} result, and to the second as the
{\sc PineAPPL} result. We repeat the computation for theories accurate to NLO
QCD and to NLO QCD+EW, respectively. In each case, we determine the PDF
uncertainty (coming from the PDF ensemble), the scale uncertainty (coming from
variations of the factorisation and renormalisation scales), and the Monte
Carlo uncertainty (coming from the finite number of events generated). In this
last respect, we consider by default high-statistics computations, whereby we
require a relative Monte Carlo precision of a fraction of permille. This choice
ensures that the statistical uncertainty of the computation is negligible
in comparison to the PDF and scale uncertainties, as we will explicitly
demonstrate.
%Add here a sentence on a low-statistics run?

Our goal is twofold. On the one hand, we aim to validate the fast interpolation
grids generated with {\sc PineAPPL}: to this purpose we shall verify that the
MC and the {\sc PineAPPL} results are identical up to numerical inaccuracies
due to the grid interpolation. This equivalence must hold for any choice of
renormalisation and factorisation scale. On the other hand, we aim to study
the size of the EW corrections, in particular with respect to the kinematics of
each process, and to an array of relative uncertainties coming from the PDFs,
the scale variations, and the experimental data.
